---
author: Nathan Swenson
title: Resume
format:
  classic-cv-pdf: default
cvfooter:
  left: "swensonnm1906@gmail.com"
  right: "github.com/swenson"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Assistant Manager for Little Caesars
    right: Lincoln, Nebraska
  - title: Field
    left: Statistics
    right: swensonnm1906@gmail.com
  - title: Techs
    left: R, bash, SAS, Python, Version Control, Tableu
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary

A community-driven and detail-oriented individual with data entry experience and an interest in statistical based projects, seeking a career as a Business Intelligence Analyst through Nelnet. Passionate about leveraging data to find optimal solutions. I aim to use my technical skills to enhance workflow and improve data analysis.

# Experience

```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Assistant Manager at Little Caesars", "Lincoln, Nebraska", "May 2022 - Present",
    "Little Caesar's, Department of Computational Social Science", c("Creating a positive environment for both colleages and customers", "Creating Schedules for my team members", "Optimizing products and time to maximize profits", "Counting Inventory and reporting back to the owner"),
    "Cofounder of the UNL STAT Club", "University of Nebraska", "Jan 2026 - Present",
    "Student Club", c("Founding of the Statistics club creating an environment of collaboration and community", "Collaborating with professors to maximize effectivity for resources and connections") 
    )|>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Bachellor's Degree in Statistics", 
    "University of Nebraska-Lincoln", 
    "Lincoln, Nebraska", 
    "Aug. 2024 - May 2028",
    c(
      "GPA: 3.810", 
      "Related Coursework: Linear Algebra, Calculus III, Principles of Study Design, Probability for Statisticians, Technical Skill for Statisticians, Statistical Computing I"),
    "High School Diploma", "Malcolm Public Schools", "Malcolm Nebraska", "Aug. 2020 - May 2024", 
  c(
    "GPA: 3.76",
    "Dual Credit Courses through Southeast Community College: Public Speaking, Psychology")
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```

# Projects

```{r }
#| label: projects
#| output: asis
tibble::tribble(
    ~name, ~purpose, ~loc, ~dates, ~details,
    "Hypergeometric Calculator Graph", "Personal", "Malcolm, Nebraska", "Jun. 2025", c(
      "Assesses the chance of drawing between 5 and 6 cards in a 40 to 60 card deck and reveals the optimal number of desired cards", 
      "Created graphics for 1 to 3 factors in Tableu"),
    "Pokemon Team Builder and Edited Chart", "Personal", "Malcolm, Nebraska", "October 2025", c(
      "Edited pokemon stats and the type chart, 
      Created an R function to test inconsistencies with pokemon's typing, 
      Used VS code to update files for a minecraft mod", 
      "Made a graphic documenting the changes through Tableu", 
      "Made a graphic for a team builder to check overall weaknesses in Tableu")
) |>
    cvevents(when = "dates", what = "name", where = "loc", details = "details")
```
